A Large-Scale Study of the Use of Eval in R

### 2020-08-23 inst/paper/main.tex
rw

>>>>

The intuition behind the soundiness manifesto~\cite{soundy} is that while
the use of a single \eval may invalidate every single invariant computed by
a static analysis or optimizer, this worst case usually does not happen.  In
many cases, \eval is used carefully and has limited effect. This is a
hypothesis that must be validated and, to be useful, we should have the
means to provide some reasonable guesses as to which side-effects will
result from any particular \eval call.
